Selecting and ranking interesting pairs of cyclic temporal granularities

### 2020-11-26 paper/main.Rmd
cleaning images

@@

gridExtra::grid.arrange(gridExtra::arrangeGrob(p1, top = paste("MMPD_norm:", round(r1, 3))),
                        gridExtra::arrangeGrob(p2, top = paste("MMPD_norm:", round(r2, 3))),
                        gridExtra::arrangeGrob(p3, top = paste("MMPD_norm:", round(r3, 3))),
                        gridExtra::arrangeGrob(p4, top = paste("MMPD_norm:", round(r4, 3))),
                        ncol = 2, nrow=2)

>>>>

r1prime <- compute_norm_pairwise_max(data1, "id_x", "id_facet", response = sim_data, nperm = 200)

r2prime <- compute_norm_pairwise_max(data2, "id_x", "id_facet", response = sim_data, nperm = 200)

r3prime <- compute_norm_pairwise_max(data3, "id_x", "id_facet", response = sim_data, nperm = 200)

r4prime <- compute_norm_pairwise_max(data4, "id_x", "id_facet", response = sim_data, nperm = 200)

@@

gridExtra::grid.arrange(gridExtra::arrangeGrob(p1, top = paste("MMPD", round(r1, 3), "pairwise", round(r1prime, 3))),
                        gridExtra::arrangeGrob(p2, top = paste("MMPD", round(r2, 3), "pairwise", round(r2prime, 3))),
                        gridExtra::arrangeGrob(p3, top = paste("MMPD", round(r3, 3), "pairwise", round(r3prime, 3))),
                        gridExtra::arrangeGrob(p4, top = paste("MMPD", round(r4, 3), "pairwise", round(r4prime, 3))),
                        ncol = 2, nrow=2)
